Smart Model Elimination for Efficient Automated Machine Learning

### 2024-06-19 paper/paper.tex
experiment design and basic table

\subsection{Experiments}

\section{Discussion}

>>>>

\section{Experiments}
\subsection{Experiment Design}
To evaluate our framework, we choose 7 different datasets of diverse size. We ran SMEML on each dataset for 32 iterations of tuning. We compared this against a "dumb" mode which simply runs every model on the dataset. We used the accuracy and time to train as our metrics.

All experiments are run on an Ubuntu server with Intel Xeon E5520 @ 2.27GHz and 24GB of RAM.

\subsection{Results}
\begin{table}
  \caption{Experiment Results}
  \label{model-options-table}
  \centering
  \begin{tabular}{llllll}
    \toprule
    % group 2, 3 as multicolumn and 4, 5 as multicolumn
    Dataset & \multicolumn{2}{c}{Accuracy} & \multicolumn{2}{c}{Time to Train} & Size (RxC)\\
    \cmidrule(lr){2-3} \cmidrule(lr){4-5}
    & SMEML & Dumb & SMEML & Dumb \\
    \midrule
    \bottomrule
  \end{tabular}
\end{table}
\section{Discussion}
